sensitivity

### 2023-06-02 scripts/workshop/sensitivity.Rmd
fix fig 5 alternate

    data[j,1:9] <- as.list(c(params.set[i,]))
    params <- params.set[i,]
    out <- as.data.frame(lsoda(xstart, times, rm0, params))
    data[j,10] <- tail(out$Ia, 1)
    data[k,11] <- tail(out$Ib, 1)s
    j <- j+1

>>>>

    data[j,1:9] <- as.list(c(params.set[i,]))
    params <- params.set[i,]
    out <- as.data.frame(lsoda(xstart, times, rm0, params))
    data[j,10] <- tail(out$Ia, 1)
    data[k,11] <- tail(out$Ib, 1)
    j <- j+1
